Draft Research pt1

### 2019-03-09 draftResearch_pt1.Rmd
Finished position eligibility

# Position Eligibility
```{r}
(get_players(50) -> tst_results)

tst_results %>%
  select(starts_with("eligible_positions")) %>%
  transpose() %>%
  lapply(as.character) %>%
  lapply(function(x) x[!is.na(x)]) -> pos_complete

# add list rows representing new column as new column on prior df?
tst_results %>%
  add_column(pos_complete) %>%
  select(1, pos_complete)

>>>>

# Position Eligibility
```{r}
get_players(450) -> players

position_columns <- players %>%
  select(starts_with("eligible_positions")) %>%
  colnames()

players %>%
  mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
  mutate(positions = gsub('NA', '', positions)) %>%
  mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
  select(-(starts_with("eligible_positions"))) %>%
  select(
    player_id:name.last, 
    editorial_team_abbr, 
    position_type, 
    display_position,
    positions
  ) -> players

players %>% saveRDS("data/players_position_eligibility.Rds")
